# Setting Up Environment

### Converting to working directory
```{r}
setwd("/Users/mohammadlotfy/Documents/csen1061-assignment-modeling")
getwd()
list.files()
```

### Set up all the needed libraries
```{r}
library("dplyr")
library("knitr")
library("partykit")
library("RWeka")
```
### First data set SONAR

```{r}
sonar.raw <- read.csv("sonar/sonar.all-data" , header = FALSE)
head(sonar.raw)
glimpse(sonar.raw)
```

# Applying multiple classifiers on SONAR
### implementing some methods
```{r}
kfolds <- function(classF) {
   kfold <- evaluate_Weka_classifier(classF, numFolds = 10)
   return(kfold)
}

getMetrics <- function(kfolds) {
  TP <- kfolds$confusionMatrix[1, 1]
  TN <- kfolds$confusionMatrix[2, 2]
  FP <- kfolds$confusionMatrix[2, 1]
  FN <- kfolds$confusionMatrix[1, 2]
  accuracy  <- (TP + TN) / (TP + TN + FP + FN)
  precision <- TP / (TP + FP)
  recall    <- TP / (TP + FN)
  f1        <- 2 * precision * recall / (precision + recall)
  res <- list(Accuracy = accuracy, Precision = precision, Recall = recall, F1 = f1)
  return(res)
}
```
### Now the classifiers

### C4.5 classifier
```{r}
sonar.c45  <- J48(V61 ~ ., sonar.raw)
print(sonar.c45)
kfolds.c45 <- kfolds(sonar.c45)
metrics.c45 <- getMetrics(kfolds.c45)
print(metrics.c45)
```

### Random Forest classifier
```{r}
random.forest <- make_Weka_classifier("weka/classifiers/trees/RandomForest")
sonar.rf <- random.forest(V1 ~ ., sonar.raw)
print(sonar.rf)
kfolds.rf <- kfolds(sonar.rf)
metrics.rf <- getMetrics(kfolds.rf)
print(metrics.rf)
```

### Support Vector Machine classifier
```{r}
sonar.svm <- SMO(V61 ~ ., sonar.raw)
kfolds.svm <- kfolds(sonar.svm)
metrics.svm <- getMetrics(kfolds.svm)
print(metrics.svm)
```

### Naive Bayes classifier
```{r}
naive.bayes <- make_Weka_classifier("weka/classifiers/bayes/NaiveBayes")
sonar.nb <- naive.bayes(V61 ~ .,sonar.raw)
kfolds.nb <- kfolds(sonar.nb)
metrics.nb <- getMetrics(kfolds.nb)
print(metrics.nb)
```

### Neural Networks
```{r}
NN <- make_Weka_classifier("weka/classifiers/functions/MultilayerPerceptron")
sonar.nn <- NN(V61 ~ ., sonar.raw)
kfolds.nn <- kfolds(sonar.nn)
metrics.nn <- getMetrics(kfolds.nn)
print(metrics.nn)
```

### Now lets do the Bagging
```{r}
sBag <- Bagging(formula(V61 ~ .,sonar.raw), sonar.raw, control = Weka_control(W = "weka.classifiers.trees.J48"), options = list(model=TRUE))
kfolds.b <- kfolds(sBag)
metrics.b <- getMetrics(kfolds.b)
print(metrics.b)
```

### AdBoost
```{r}
sonar.adBoost <- AdaBoostM1(V61 ~.,sonar.raw)
kfolds.adBoost <- kfolds(sonar.adBoost)
metrics.adBoost <- getMetrics(kfolds.adBoost)
print(metrics.adBoost)
```

# Getting the other datasets

### spect, pima and hepatitis
```{r}
hepatitis.raw <- read.csv("hepatitis/hepatitis.data", header = FALSE) %>% mutate(V1 = as.factor(V1))
spect.raw <-  rbind(read.csv("spect/SPECT.train", header = FALSE), read.csv("spect/SPECT.test", header = FALSE)) %>% mutate(V1 = as.factor(V1))
pima.raw <- read.csv("pima/pima-indians-diabetes.data", header = FALSE) %>% rename(V1 = V9, V9 = V1) %>% mutate(V1 = as.factor(V1))
```

### hepatitis and c4.5 test 10 times matrix
```{r}
hepatitis.c4.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(hepatitis.c4.set) <- c("Accuracy","Precision","Recall","F1")
for(i in 1:10){
  temp.c45  <- J48(V1 ~ ., hepatitis.raw)
  kfolds.c45 <- kfolds(temp.c45)
  metrics.c45 <- getMetrics(kfolds.c45)
  hepatitis.c4.set[i,]$Accuracy <- metrics.c45$Accuracy
  hepatitis.c4.set[i,]$Precision <- metrics.c45$Precision
  hepatitis.c4.set[i,]$Recall <- metrics.c45$Recall
  hepatitis.c4.set[i,]$F1 <- metrics.c45$F1
}
hepatitis.c4.set
```

### hepatitis and random forest 10 times matrix
```{r}
hepatitis.RF.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(hepatitis.RF.set) <- c("Accuracy","Precision","Recall","F1")
for(i in 1:10){
  temp.RF  <- random.forest(V1 ~ ., hepatitis.raw)
  kfolds.RF <- kfolds(temp.RF)
  metrics.RF <- getMetrics(kfolds.RF)
  hepatitis.RF.set[i,]$Accuracy <- metrics.RF$Accuracy
  hepatitis.RF.set[i,]$Precision <- metrics.RF$Precision
  hepatitis.RF.set[i,]$Recall <- metrics.RF$Recall
  hepatitis.RF.set[i,]$F1 <- metrics.RF$F1
}
hepatitis.RF.set
```

### hepatitis and SVM classifier 10 times
```{r}
hepatitis.SVM.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(hepatitis.SVM.set) <- c("Accuracy","Precision","Recall","F1")
for(i in 1:10){
  temp  <- SMO(V1 ~ ., hepatitis.raw)
  kfolds.t <- kfolds(temp)
  metrics <- getMetrics(kfolds.t)
  hepatitis.SVM.set[i,]$Accuracy <- metrics$Accuracy
  hepatitis.SVM.set[i,]$Precision <- metrics$Precision
  hepatitis.SVM.set[i,]$Recall <- metrics$Recall
  hepatitis.SVM.set[i,]$F1 <- metrics$F1
}
hepatitis.SVM.set
```
#### hepatitis and naive bayes 10 times
```{r}
hepatitis.NB.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(hepatitis.NB.set) <- c("Accuracy","Precision","Recall","F1")
for(i in 1:10){
  temp  <- naive.bayes(V1 ~ ., hepatitis.raw)
  kfolds.t <- kfolds(temp)
  metrics <- getMetrics(kfolds.t)
  hepatitis.NB.set[i,]$Accuracy <- metrics$Accuracy
  hepatitis.NB.set[i,]$Precision <- metrics$Precision
  hepatitis.NB.set[i,]$Recall <- metrics$Recall
  hepatitis.NB.set[i,]$F1 <- metrics$F1
}
hepatitis.NB.set
```

### hepatitis and bagging 10 times
```{r}
hBag <- Bagging(formula(V1 ~ .,hepatitis.raw), hepatitis.raw, control = Weka_control(W = "weka.classifiers.trees.J48"), options = list(model=TRUE))
hepatitis.BAG.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(hepatitis.BAG.set) <- c("Accuracy","Precision","Recall","F1")
for(i in 1:10){
  kfolds.t <- kfolds(hBag)
  metrics <- getMetrics(kfolds.t)
  hepatitis.BAG.set[i,]$Accuracy <- metrics$Accuracy
  hepatitis.BAG.set[i,]$Precision <- metrics$Precision
  hepatitis.BAG.set[i,]$Recall <- metrics$Recall
  hepatitis.BAG.set[i,]$F1 <- metrics$F1
}
hepatitis.BAG.set
```

### hepatitis and boosting 10 times
```{r}
hepatitis.BOOST.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(hepatitis.BOOST.set) <- c("Accuracy","Precision","Recall","F1")
for(i in 1:10){
  h.adBoost <- AdaBoostM1(V1 ~.,hepatitis.raw)
  kfolds.t <- kfolds(h.adBoost)
  metrics <- getMetrics(kfolds.t)
  hepatitis.BOOST.set[i,]$Accuracy <- metrics$Accuracy
  hepatitis.BOOST.set[i,]$Precision <- metrics$Precision
  hepatitis.BOOST.set[i,]$Recall <- metrics$Recall
  hepatitis.BOOST.set[i,]$F1 <- metrics$F1
}
hepatitis.BOOST.set
```

### hepatitis and MultilayerPerceptron 10 times
It will take a while longer than the other classifiers and it caused my R console to not respond! thats why I commented it.
```{r}
#NN <- make_Weka_classifier("weka/classifiers/functions/MultilayerPerceptron")
#hepatitis.nn <- NN(V1 ~ ., hepatitis.raw)
#hepatitis.NN.set <- data.frame(matrix(ncol = 4, nrow = 10))
#names(hepatitis.NN.set) <- c("Accuracy","Precision","Recall","F1")
#for(i in 1:10){
#  kfolds.t <- kfolds(hepatitis.nn)
#  metrics <- getMetrics(kfolds.t)
#  hepatitis.NN.set[i,]$Accuracy <- metrics$Accuracy
#  hepatitis.NN.set[i,]$Precision <- metrics$Precision
#  hepatitis.NN.set[i,]$Recall <- metrics$Recall
#  hepatitis.NN.set[i,]$F1 <- metrics$F1
#}
#hepatitis.NN.set
```

### instead of doing each loop separately we can do all of them at one loop for spect dataset

```{r}
spect.c4.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(spect.c4.set) <- c("Accuracy","Precision","Recall","F1")

spect.RF.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(spect.RF.set) <- c("Accuracy","Precision","Recall","F1")

spect.SVM.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(spect.SVM.set) <- c("Accuracy","Precision","Recall","F1")

spect.NB.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(spect.NB.set) <- c("Accuracy","Precision","Recall","F1")

spect.BAG.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(spect.BAG.set) <- c("Accuracy","Precision","Recall","F1")

spectBag <- Bagging(formula(V1 ~ .,spect.raw), spect.raw, control = Weka_control(W = "weka.classifiers.trees.J48"), options = list(model=TRUE))

spect.BOOST.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(spect.BOOST.set) <- c("Accuracy","Precision","Recall","F1")

for(i in 1:10){
  temp.c45  <- J48(V1 ~ ., spect.raw)
  kfolds.c45 <- kfolds(temp.c45)
  metrics.c45 <- getMetrics(kfolds.c45)
  spect.c4.set[i,]$Accuracy <- metrics.c45$Accuracy
  spect.c4.set[i,]$Precision <- metrics.c45$Precision
  spect.c4.set[i,]$Recall <- metrics.c45$Recall
  spect.c4.set[i,]$F1 <- metrics.c45$F1

  temp.RF  <- random.forest(V1 ~ ., spect.raw)
  kfolds.RF <- kfolds(temp.RF)
  metrics.RF <- getMetrics(kfolds.RF)
  spect.RF.set[i,]$Accuracy <- metrics.RF$Accuracy
  spect.RF.set[i,]$Precision <- metrics.RF$Precision
  spect.RF.set[i,]$Recall <- metrics.RF$Recall
  spect.RF.set[i,]$F1 <- metrics.RF$F1

  temp.sv  <- SMO(V1 ~ ., spect.raw)
  kfolds.t <- kfolds(temp.sv)
  metrics <- getMetrics(kfolds.t)
  spect.SVM.set[i,]$Accuracy <- metrics$Accuracy
  spect.SVM.set[i,]$Precision <- metrics$Precision
  spect.SVM.set[i,]$Recall <- metrics$Recall
  spect.SVM.set[i,]$F1 <- metrics$F1

  temp.nb  <- naive.bayes(V1 ~ ., spect.raw)
  kfolds.t <- kfolds(temp.nb)
  metrics <- getMetrics(kfolds.t)
  spect.NB.set[i,]$Accuracy <- metrics$Accuracy
  spect.NB.set[i,]$Precision <- metrics$Precision
  spect.NB.set[i,]$Recall <- metrics$Recall
  spect.NB.set[i,]$F1 <- metrics$F1

  kfolds.t <- kfolds(spectBag)
  metrics <- getMetrics(kfolds.t)
  spect.BAG.set[i,]$Accuracy <- metrics$Accuracy
  spect.BAG.set[i,]$Precision <- metrics$Precision
  spect.BAG.set[i,]$Recall <- metrics$Recall
  spect.BAG.set[i,]$F1 <- metrics$F1

  spect.adBoost <- AdaBoostM1(V1 ~.,spect.raw)
  kfolds.t <- kfolds(spect.adBoost)
  metrics <- getMetrics(kfolds.t)
  spect.BOOST.set[i,]$Accuracy <- metrics$Accuracy
  spect.BOOST.set[i,]$Precision <- metrics$Precision
  spect.BOOST.set[i,]$Recall <- metrics$Recall
  spect.BOOST.set[i,]$F1 <- metrics$F1
}
spect.c4.set
spect.RF.set
spect.SVM.set
spect.NB.set
spect.BAG.set
spect.BOOST.set
```
### we can do the same thing for the pima data set

```{r}
pima.c4.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(pima.c4.set) <- c("Accuracy","Precision","Recall","F1")

pima.RF.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(pima.RF.set) <- c("Accuracy","Precision","Recall","F1")

pima.SVM.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(pima.SVM.set) <- c("Accuracy","Precision","Recall","F1")

pima.NB.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(pima.NB.set) <- c("Accuracy","Precision","Recall","F1")

pima.BAG.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(pima.BAG.set) <- c("Accuracy","Precision","Recall","F1")

pimaBag <- Bagging(formula(V1 ~ .,pima.raw), pima.raw, control = Weka_control(W = "weka.classifiers.trees.J48"), options = list(model=TRUE))

pima.BOOST.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(pima.BOOST.set) <- c("Accuracy","Precision","Recall","F1")

for(i in 1:10){
  temp.c45  <- J48(V1 ~ ., pima.raw)
  kfolds.c45 <- kfolds(temp.c45)
  metrics.c45 <- getMetrics(kfolds.c45)
  pima.c4.set[i,]$Accuracy <- metrics.c45$Accuracy
  pima.c4.set[i,]$Precision <- metrics.c45$Precision
  pima.c4.set[i,]$Recall <- metrics.c45$Recall
  pima.c4.set[i,]$F1 <- metrics.c45$F1

  temp.RF  <- random.forest(V1 ~ ., pima.raw)
  kfolds.RF <- kfolds(temp.RF)
  metrics.RF <- getMetrics(kfolds.RF)
  pima.RF.set[i,]$Accuracy <- metrics.RF$Accuracy
  pima.RF.set[i,]$Precision <- metrics.RF$Precision
  pima.RF.set[i,]$Recall <- metrics.RF$Recall
  pima.RF.set[i,]$F1 <- metrics.RF$F1

  temp.sv  <- SMO(V1 ~ ., pima.raw)
  kfolds.t <- kfolds(temp.sv)
  metrics <- getMetrics(kfolds.t)
  pima.SVM.set[i,]$Accuracy <- metrics$Accuracy
  pima.SVM.set[i,]$Precision <- metrics$Precision
  pima.SVM.set[i,]$Recall <- metrics$Recall
  pima.SVM.set[i,]$F1 <- metrics$F1

  temp.nb  <- naive.bayes(V1 ~ ., pima.raw)
  kfolds.t <- kfolds(temp.nb)
  metrics <- getMetrics(kfolds.t)
  pima.NB.set[i,]$Accuracy <- metrics$Accuracy
  pima.NB.set[i,]$Precision <- metrics$Precision
  pima.NB.set[i,]$Recall <- metrics$Recall
  pima.NB.set[i,]$F1 <- metrics$F1

  kfolds.t <- kfolds(pimaBag)
  metrics <- getMetrics(kfolds.t)
  pima.BAG.set[i,]$Accuracy <- metrics$Accuracy
  pima.BAG.set[i,]$Precision <- metrics$Precision
  pima.BAG.set[i,]$Recall <- metrics$Recall
  pima.BAG.set[i,]$F1 <- metrics$F1

  pima.adBoost <- AdaBoostM1(V1 ~.,pima.raw)
  kfolds.t <- kfolds(pima.adBoost)
  metrics <- getMetrics(kfolds.t)
  pima.BOOST.set[i,]$Accuracy <- metrics$Accuracy
  pima.BOOST.set[i,]$Precision <- metrics$Precision
  pima.BOOST.set[i,]$Recall <- metrics$Recall
  pima.BOOST.set[i,]$F1 <- metrics$F1
}
pima.c4.set
pima.RF.set
pima.SVM.set
pima.NB.set
pima.BAG.set
pima.BOOST.set
```

### and at last lets do it for the very first data set sonar
```{r}
sonar.c4.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(sonar.c4.set) <- c("Accuracy","Precision","Recall","F1")

sonar.RF.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(sonar.RF.set) <- c("Accuracy","Precision","Recall","F1")

sonar.SVM.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(sonar.SVM.set) <- c("Accuracy","Precision","Recall","F1")

sonar.NB.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(sonar.NB.set) <- c("Accuracy","Precision","Recall","F1")

sonar.BAG.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(sonar.BAG.set) <- c("Accuracy","Precision","Recall","F1")

sonarBag <- Bagging(formula(V61 ~ .,sonar.raw), sonar.raw, control = Weka_control(W = "weka.classifiers.trees.J48"), options = list(model=TRUE))

sonar.BOOST.set <- data.frame(matrix(ncol = 4, nrow = 10))
names(sonar.BOOST.set) <- c("Accuracy","Precision","Recall","F1")

for(i in 1:10){
  temp.c45  <- J48(V61 ~ ., sonar.raw)
  kfolds.c45 <- kfolds(temp.c45)
  metrics.c45 <- getMetrics(kfolds.c45)
  sonar.c4.set[i,]$Accuracy <- metrics.c45$Accuracy
  sonar.c4.set[i,]$Precision <- metrics.c45$Precision
  sonar.c4.set[i,]$Recall <- metrics.c45$Recall
  sonar.c4.set[i,]$F1 <- metrics.c45$F1

  temp.RF  <- random.forest(V61 ~ ., sonar.raw)
  kfolds.RF <- kfolds(temp.RF)
  metrics.RF <- getMetrics(kfolds.RF)
  sonar.RF.set[i,]$Accuracy <- metrics.RF$Accuracy
  sonar.RF.set[i,]$Precision <- metrics.RF$Precision
  sonar.RF.set[i,]$Recall <- metrics.RF$Recall
  sonar.RF.set[i,]$F1 <- metrics.RF$F1

  temp.sv  <- SMO(V61 ~ ., sonar.raw)
  kfolds.t <- kfolds(temp.sv)
  metrics <- getMetrics(kfolds.t)
  sonar.SVM.set[i,]$Accuracy <- metrics$Accuracy
  sonar.SVM.set[i,]$Precision <- metrics$Precision
  sonar.SVM.set[i,]$Recall <- metrics$Recall
  sonar.SVM.set[i,]$F1 <- metrics$F1

  temp.nb  <- naive.bayes(V61 ~ ., sonar.raw)
  kfolds.t <- kfolds(temp.nb)
  metrics <- getMetrics(kfolds.t)
  sonar.NB.set[i,]$Accuracy <- metrics$Accuracy
  sonar.NB.set[i,]$Precision <- metrics$Precision
  sonar.NB.set[i,]$Recall <- metrics$Recall
  sonar.NB.set[i,]$F1 <- metrics$F1

  kfolds.t <- kfolds(sonarBag)
  metrics <- getMetrics(kfolds.t)
  sonar.BAG.set[i,]$Accuracy <- metrics$Accuracy
  sonar.BAG.set[i,]$Precision <- metrics$Precision
  sonar.BAG.set[i,]$Recall <- metrics$Recall
  sonar.BAG.set[i,]$F1 <- metrics$F1

  sonar.adBoost <- AdaBoostM1(V61 ~.,sonar.raw)
  kfolds.t <- kfolds(pima.adBoost)
  metrics <- getMetrics(kfolds.t)
  sonar.BOOST.set[i,]$Accuracy <- metrics$Accuracy
  sonar.BOOST.set[i,]$Precision <- metrics$Precision
  sonar.BOOST.set[i,]$Recall <- metrics$Recall
  sonar.BOOST.set[i,]$F1 <- metrics$F1
}
sonar.c4.set
sonar.RF.set
sonar.SVM.set
sonar.NB.set
sonar.BAG.set
sonar.BOOST.set
```
# Comparisons
### As I see it we have to compare every two classifiers for a certain metric on the same dataset

## Sonar

### Accuracy Metric
```{r}
accuracy_c4_RF_sonar <- t.test(sonar.c4.set$Accuracy,sonar.RF.set$Accuracy)
accuracy_RF_SVM_sonar <- t.test(sonar.RF.set$Accuracy,sonar.SVM.set$Accuracy)
accuracy_SVM_NB_sonar <- t.test(sonar.SVM.set$Accuracy,sonar.NB.set$Accuracy)
accuracy_NB_BAG_sonar <- t.test(sonar.NB.set$Accuracy,sonar.BAG.set$Accuracy)
accuracy_BAG_BOOST_sonar <- t.test(sonar.BAG.set$Accuracy,sonar.BOOST.set$Accuracy)
```
### Precision
```{r}
precision_c4_RF_sonar <- t.test(sonar.c4.set$Precision,sonar.RF.set$Precision)
precision_RF_SVM_sonar <- t.test(sonar.RF.set$Precision,sonar.SVM.set$Precision)
precision_SVM_NB_sonar <- t.test(sonar.SVM.set$Precision,sonar.NB.set$Precision)
precision_NB_BAG_sonar <- t.test(sonar.NB.set$Precision,sonar.BAG.set$Precision)
precision_BAG_BOOST_sonar <- t.test(sonar.BAG.set$Precision,sonar.BOOST.set$Precision)
```

### Recall
```{r}
recall_c4_RF_sonar <- t.test(sonar.c4.set$Recall,sonar.RF.set$Recall)
recall_RF_SVM_sonar <- t.test(sonar.RF.set$Recall,sonar.SVM.set$Recall)
recall_SVM_NB_sonar <- t.test(sonar.SVM.set$Recall,sonar.NB.set$Recall)
recall_NB_BAG_sonar <- t.test(sonar.NB.set$Recall,sonar.BAG.set$Recall)
recall_BAG_BOOST_sonar <- t.test(sonar.BAG.set$Recall,sonar.BOOST.set$Recall)
```

### F-Score
```{r}
F1_c4_RF_sonar <- t.test(sonar.c4.set$F1,sonar.RF.set$F1)
F1_RF_SVM_sonar <- t.test(sonar.RF.set$F1,sonar.SVM.set$F1)
F1_SVM_NB_sonar <- t.test(sonar.SVM.set$F1,sonar.NB.set$F1)
F1_NB_BAG_sonar <- t.test(sonar.NB.set$F1,sonar.BAG.set$F1)
F1_BAG_BOOST_sonar <- t.test(sonar.BAG.set$F1,sonar.BOOST.set$F1)
```

## hepatitis

```{r}
accuracy_c4_RF_hepatitis <- t.test(hepatitis.c4.set$Accuracy,hepatitis.RF.set$Accuracy)
accuracy_RF_SVM_hepatitis <- t.test(hepatitis.RF.set$Accuracy,hepatitis.SVM.set$Accuracy)
accuracy_SVM_NB_hepatitis <- t.test(hepatitis.SVM.set$Accuracy,hepatitis.NB.set$Accuracy)
accuracy_NB_BAG_hepatitis <- t.test(hepatitis.NB.set$Accuracy,hepatitis.BAG.set$Accuracy)
accuracy_BAG_BOOST_hepatitis <- t.test(hepatitis.BAG.set$Accuracy,hepatitis.BOOST.set$Accuracy)

precision_c4_RF_hepatitis <- t.test(hepatitis.c4.set$Precision,hepatitis.RF.set$Precision)
precision_RF_SVM_hepatitis <- t.test(hepatitis.RF.set$Precision,hepatitis.SVM.set$Precision)
precision_SVM_NB_hepatitis <- t.test(hepatitis.SVM.set$Precision,hepatitis.NB.set$Precision)
precision_NB_BAG_hepatitis <- t.test(hepatitis.NB.set$Precision,hepatitis.BAG.set$Precision)
precision_BAG_BOOST_hepatitis <- t.test(hepatitis.BAG.set$Precision,hepatitis.BOOST.set$Precision)

recall_c4_RF_hepatitis <- t.test(hepatitis.c4.set$Recall,hepatitis.RF.set$Recall)
recall_RF_SVM_hepatitis <- t.test(hepatitis.RF.set$Recall,hepatitis.SVM.set$Recall)
recall_SVM_NB_hepatitis <- t.test(hepatitis.SVM.set$Recall,hepatitis.NB.set$Recall)
recall_NB_BAG_hepatitis <- t.test(hepatitis.NB.set$Recall,hepatitis.BAG.set$Recall)
recall_BAG_BOOST_hepatitis <- t.test(hepatitis.BAG.set$Recall,hepatitis.BOOST.set$Recall)

F1_c4_RF_hepatitis <- t.test(hepatitis.c4.set$F1,hepatitis.RF.set$F1)
F1_RF_SVM_hepatitis <- t.test(hepatitis.RF.set$F1,hepatitis.SVM.set$F1)
F1_SVM_NB_hepatitis <- t.test(hepatitis.SVM.set$F1,hepatitis.NB.set$F1)
F1_NB_BAG_hepatitis <- t.test(hepatitis.NB.set$F1,hepatitis.BAG.set$F1)
F1_BAG_BOOST_hepatitis <- t.test(hepatitis.BAG.set$F1,hepatitis.BOOST.set$F1)
```

## pima

```{r}
accuracy_c4_RF_pima <- t.test(pima.c4.set$Accuracy,pima.RF.set$Accuracy)
accuracy_RF_SVM_pima <- t.test(pima.RF.set$Accuracy,pima.SVM.set$Accuracy)
accuracy_SVM_NB_pima <- t.test(pima.SVM.set$Accuracy,pima.NB.set$Accuracy)
accuracy_NB_BAG_pima <- t.test(pima.NB.set$Accuracy,pima.BAG.set$Accuracy)
accuracy_BAG_BOOST_pima <- t.test(pima.BAG.set$Accuracy,pima.BOOST.set$Accuracy)

precision_c4_RF_pima <- t.test(pima.c4.set$Precision,pima.RF.set$Precision)
precision_RF_SVM_pima <- t.test(pima.RF.set$Precision,pima.SVM.set$Precision)
precision_SVM_NB_pima <- t.test(pima.SVM.set$Precision,pima.NB.set$Precision)
precision_NB_BAG_pima <- t.test(pima.NB.set$Precision,pima.BAG.set$Precision)
precision_BAG_BOOST_pima <- t.test(pima.BAG.set$Precision,pima.BOOST.set$Precision)

recall_c4_RF_pima <- t.test(pima.c4.set$Recall,pima.RF.set$Recall)
recall_RF_SVM_pima <- t.test(pima.RF.set$Recall,pima.SVM.set$Recall)
recall_SVM_NB_pima <- t.test(pima.SVM.set$Recall,pima.NB.set$Recall)
recall_NB_BAG_pima <- t.test(pima.NB.set$Recall,pima.BAG.set$Recall)
recall_BAG_BOOST_pima <- t.test(pima.BAG.set$Recall,pima.BOOST.set$Recall)

F1_c4_RF_pima <- t.test(pima.c4.set$F1,pima.RF.set$F1)
F1_RF_SVM_pima<- t.test(pima.RF.set$F1,pima.SVM.set$F1)
F1_SVM_NB_pima <- t.test(pima.SVM.set$F1,pima.NB.set$F1)
F1_NB_BAG_pima <- t.test(pima.NB.set$F1,pima.BAG.set$F1)
F1_BAG_BOOST_pima<- t.test(pima.BAG.set$F1,pima.BOOST.set$F1)
```

##spect
```{r}
accuracy_c4_RF_spect<- t.test(spect.c4.set$Accuracy,spect.RF.set$Accuracy)
accuracy_RF_SVM_spect <- t.test(spect.RF.set$Accuracy,spect.SVM.set$Accuracy)
accuracy_SVM_NB_spect<- t.test(spect.SVM.set$Accuracy,spect.NB.set$Accuracy)
accuracy_NB_BAG_spect <- t.test(spect.NB.set$Accuracy,spect.BAG.set$Accuracy)
accuracy_BAG_BOOST_spect <- t.test(spect.BAG.set$Accuracy,spect.BOOST.set$Accuracy)

precision_c4_RF_spect <- t.test(spect.c4.set$Precision,spect.RF.set$Precision)
precision_RF_SVM_spect <- t.test(spect.RF.set$Precision,spect.SVM.set$Precision)
precision_SVM_NB_spect <- t.test(spect.SVM.set$Precision,spect.NB.set$Precision)
precision_NB_BAG_spect <- t.test(spect.NB.set$Precision,spect.BAG.set$Precision)
precision_BAG_BOOST_spect <- t.test(spect.BAG.set$Precision,spect.BOOST.set$Precision)

recall_c4_RF_spect <- t.test(spect.c4.set$Recall,spect.RF.set$Recall)
recall_RF_SVM_spect<- t.test(spect.RF.set$Recall,spect.SVM.set$Recall)
recall_SVM_NB_spect <- t.test(spect.SVM.set$Recall,spect.NB.set$Recall)
recall_NB_BAG_spect <- t.test(spect.NB.set$Recall,spect.BAG.set$Recall)
recall_BAG_BOOST_spect <- t.test(spect.BAG.set$Recall,spect.BOOST.set$Recall)

F1_c4_RF_spect <- t.test(spect.c4.set$F1,spect.RF.set$F1)
F1_RF_SVM_spect <- t.test(spect.RF.set$F1,spect.SVM.set$F1)
F1_SVM_NB_spect <- t.test(spect.SVM.set$F1,spect.NB.set$F1)
F1_NB_BAG_spect <- t.test(spect.NB.set$F1,spect.BAG.set$F1)
F1_BAG_BOOST_spect <- t.test(spect.BAG.set$F1,spect.BOOST.set$F1)
```
